He-Man: A domain-specific language for lightweight concurrency

### 2011-12-12 report/report.tex
papering

@@

\section{Performance}

Each thread takes up XXX memory (see Memory.hs)

>>>>

%XXX: abstract

@@

\section{Evaluation}

The per-thread memory overhead imposed by He-Man is very small: it
consists of a thread id, list pointers for the scheduling queue, the
next state to enter, a pointer to the most recently received event,
and list heads and tails for lists of the events being waited on,
events owned by the thread, and buffers owned by the thread (the
latter two are so that we can automatically reclaim these resources
when the thread exits). On a 64-bit system, the total overhead comes
out to 88 bytes, and could easily be reduced further (e.g. by using
singly linked lists).  For comparison, the default thread stack size
under NPTL on Linux is 2 megabytes.

say something about Memory.hs
each thread takes up XXX memory (see Memory.hs)

To evaluate He-Man,
